% LaTeX file for Naim Lujan resume 

\documentclass{res} 
\textwidth=5.2in 
\newsectionwidth{0pt}  
%\usepackage{helvetica} 
%\usepackage{newcent}   
\usepackage{enumitem}
\usepackage{bbding}
\usepackage{tikz}
\usepackage{pifont}
\usepackage{latexsym}
\usepackage{hyperref}

\begin{document} 
 
\name{ {\LARGE Naim J. Luj\'{a}n}\\[8pt]} 
 
\address{\href{http://naimlujan.com}{naimlujan.com} \\  \href{https://github.com/nlujan}{github:  \hspace*{0.5mm}nlujan}  }
\address{\hspace*{4mm} (956) 369-7286 \\ \href{mailto:naim.lujan@gmail.com}{naim.lujan@gmail} }

\begin{resume} 

\moveleft\hoffset\vbox{\hrule width\resumewidth height 2pt}\smallskip 
 
\vspace{-5pt}

\section{{\large Education} } 

\vspace{-10pt}

\noindent\rule{\resumewidth}{0.4pt}  

\vspace{-5pt}

{\bf Massachusetts Institute of Technology} \hfill {\bf Cambridge, MA} \\
{\textit {S.B. in Computer Science and Engineering}} \hfill {\textit {June 2015}} \\
\vspace{-10pt}
\begin{itemize}
\renewcommand{\labelitemi}{\ding{117}}
\itemsep -2pt  
\item Coursework: Algorithms, Software Construction, Computer Systems Engineering,  
Computation Structures, Artificial Intelligence, Computer Security, Web Programming, Computational Photography

\end{itemize}

\section{{\large Experience}}

\vspace{-10pt}

\noindent\rule{\resumewidth}{0.4pt}   

\vspace{-5pt}

 %Two Bulls
{\bf MoviePass} \hfill {\bf New York, NY} \\
{\textit {Senior iOS Engineer}} \hfill {\textit {Dec 2017 - Present}} 
\begin{itemize}
\renewcommand{\labelitemi}{\ding{117}}
\itemsep -2pt  
\item Built iOS Swift app from the ground up as user base grew from 50K to over 3M.
\item Collaborated with product, design, and backend teams to constantly build new features and overcome challenges stemming from rapid growth and evolving business needs.
\item Led growth of team through interviewing, onboarding, and mentoring of new iOS engineers. 
\end{itemize}

 %Freelancer
{\bf Freelancer} \hfill {\bf New York, NY} \\
{\textit {iOS Engineer}} \hfill {\textit {Aug 2017 - Dec 2017}} 
\begin{itemize}
\renewcommand{\labelitemi}{\ding{117}}
\itemsep -2pt  
\item Developed new features for an iOS Swift app which delivers treats on demand to thousands of users.
\end{itemize}

 %Two Bulls
{\bf Two Bulls} \hfill {\bf New York, NY} \\
{\textit {Mobile Engineer}} \hfill {\textit {Nov 2016 - Sept 2017}} 
\begin{itemize}
\renewcommand{\labelitemi}{\ding{117}}
\itemsep -2pt  
\item Built iOS Swift app with AWS Serverless backend that facilitates the managing of kitchen appliances through Estimote Bluetooth beacons. 
\item Worked on several Android Kotlin applications that run on large multi-screen kiosks, which allow the community to discover points of interest, find directions via public transit or ride sharing, make calls, and see popular social media in the area. 
\item Developed Android Java cover screen app with Django backend which allows users to like/dislike ads in return for carrier reward points.

\end{itemize}

 %Integral Ad Science
{\bf Integral Ad Science} \hfill {\bf New York, NY} \\
{\textit {Software Engineer}} \hfill {\textit {Nov 2015 - Oct 2016}} 
\begin{itemize}
\renewcommand{\labelitemi}{\ding{117}}
\itemsep -2pt  
\item Worked on a small agile team developing, testing, and maintaining a range of video ad solutions from html5 video player ad integrations to video viewability detection.
\item Collaborated with different teams across the technological stack to develop and maintain a wide range of features of our ad software solutions.
\item Developed bot detection algorithms and other features for ad fraud prevention.

\end{itemize}

%Qualcomm
{\bf Qualcomm} \hfill {\bf San Diego, CA} \\
{\textit {Software Engineer}} \hfill {\textit {Jun 2013 - Aug 2013}} 
\begin{itemize} 
\renewcommand{\labelitemi}{\ding{117}}
\itemsep -2pt  
\item Built Python GUI tool that expedites the creation of software 
	change requests through API calls and sophisticated data manipulation.
\item Implemented enhanced data analysis features of a Data Miner in C that
	 improves the accuracy of RF software implementations.
\end{itemize}

% %Labatt Food Service
%{\bf Labatt Food Service} \hfill {\bf San Antonio, TX} \\
%{\textit {Software Development Intern}} \hfill {\textit {Jun 2012 - Aug 2012}} 
%\begin{itemize}
%\renewcommand{\labelitemi}{\ding{117}}
%\itemsep -2pt  
%%\item Built web application using ASP.NET to analyze data, determine key limitations of
%%	forecast system, and develop algorithmic hypotheses.
%\item Implemented forecasting algorithms in VB.NET to accurately predict product demand
%	and overcome pitfalls of previous system.
%\end{itemize}

\vspace{-9pt}

\section{{\large Skills/Interests}}

\vspace{-10pt}

\noindent\rule{\resumewidth}{0.4pt}  
\vspace{-30pt}
\begin{tabbing}
{\bf Technical: } ~~~~~~~~~ \= Swift, iOS, Python, Java, Kotlin, Android, Javascript, C++ \\
\> AWS, Serverless, MEAN, Django, Elm, MATLAB, \LaTeX \\
{\bf Academic: } \>  Mobile Development, Computer Security, Web Development \\
{\bf Language: } \> English, Spanish, Portuguese\\
{\bf Extracurricular: } \> Soccer, Theta Chi Fraternity, Cryptocurrency \\
\end{tabbing}

\end{resume} 
\end{document} 
